\documentclass[12pt,english,hyperfootnotes=false,hidelinks]{article}

%%%% Packages
\usepackage{lmodern}
\usepackage{tablefootnote}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=1.25in,bmargin=1.25in,lmargin=1.25in,rmargin=1.25in}
\usepackage{float}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[authoryear]{natbib}
\usepackage[bottom,multiple]{footmisc}
\usepackage{geometry}
\usepackage{adjustbox}
\usepackage[hyphenbreaks]{breakurl}
\usepackage{booktabs}
\usepackage{pdflscape}
\usepackage{siunitx}
\usepackage{numprint}
\usepackage{threeparttable}
\usepackage{caption}
\usepackage{babel}
\usepackage{xcolor}
\usepackage{longtable}
\usepackage{afterpage}
\usepackage{dcolumn}
\usepackage{multicol}
\usepackage{amsfonts}
\usepackage{adjustbox}
\usepackage{xurl}
\usepackage{hyperref}
\usepackage{catchfilebetweentags}
\usepackage{csquotes}
\usepackage{framed}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\usepackage{makecell}
\usepackage{natbib}
% define check and xmark
\usepackage{pifont}
\usepackage{textcomp}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

%%%% Other settings
\captionsetup[table]{skip=0pt}
\interfootnotelinepenalty=10000
\newcolumntype{R}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}

\newtheorem{assumption}{Assumption}
\newtheorem{hyp}{Hypothesis}
\newtheorem{proposition}{Proposition}

%%% Command for extracting numbers
\newcommand{\gn}[1]{\ExecuteMetaData[results/results.tex]{#1}}



\title{
Can Direct Micropayment Incentives Shape the Quality of Online Discourse?\thanks{
The views expressed in this paper are solely those of the authors and do not necessarily reflect the views of Stacker News. Stacker News provided the data, but did not exercise editorial control over the content of this paper, nor over the analysis, interpretation, or reporting of the results. All errors are those of the authors. 
Corresponding author: Edward Kung, Department of Economics, California State University-Northridge, \url{edward.kung@csun.edu}. All computer code used for the analysis is open source and available at \url{https://github.com/ed-kung/sn-research}.
}
}

\author{
    Edward Kung\\CSUN\\edward.kung@csun.edu \and
    Keyan Kousha\\Stacker News\\kk@stacker.news
}

\date{\today}

\begin{document}

\maketitle

\singlespacing

\vspace{-1cm}

\begin{abstract}
This paper studies how small posting fees and peer-to-peer monetary rewards shape the quality and quantity of posts in online discourse. The setting is an online discussion platform that uses Bitcoin micropayments. On the platform, users must pay a small fee to post content and can earn peer-to-peer tips from other users who value their contributions. Using variation in posting fees across the platform's sub-forums and over time, we estimate how post quantity and quality change after a posting fee change. We find that the number of posts responds negatively to a posting fee increase, with an elasticity of $\gn{PostsCostElasticity}$, but that the quality of posts, as measured by tips earned, responds positively to a posting fee increase, with an elasticity of $\gn{Zaps48CostElasticity}$. These results are consistent with a screening model in which posting costs filter out low-quality contributions. We also find evidence that users adjust subsequent posting behavior in response to observed tip-based feedback, and that users who do not recover their posting costs through tips are more likely to exit the platform.  These findings provide empirical evidence on how small financial incentives can shape the quantity and quality of online discussion.
\end{abstract}


\noindent{\textit{Keywords}: micropayments; user-generated content; signaling; market design; digital platforms} \\
\noindent {\textit{JEL Classification}: D82, D83, L86} \\


\doublespacing

\pagebreak

\input{01intro}
\input{02incentives}
\input{04data}
\input{05paytopost}
\input{06v4v}
\input{07profitability}
\input{08conclusion}

\bibliographystyle{chicago}
\bibliography{91refs}

\pagebreak
\input{results/fig_weekly_items.tex}
\pagebreak
\input{results/fig_territory_posting_fees.tex}
\pagebreak
\input{results/fig_post_quality_event_study.tex}
\pagebreak
\input{results/fig_post_quantity_event_study.tex}
\pagebreak
\input{results/fig_v4v_q_trend}

\pagebreak
\input{results/tbl_sats48_cost_reg} 
\pagebreak
\input{results/tbl_posts_cost_reg} 
\pagebreak
\input{results/tbl_post_types_summary}
\pagebreak
\input{results/tbl_learning}
\pagebreak
\input{results/tbl_profitability_analysis}

\pagebreak

\appendix

\section*{Online Appendix}

\input{94appendix}

\end{document}

