\section{Introduction} \label{sec_intro}

Can direct financial incentives shape the quality of online discourse?  A large literature has studied how indirect mechanisms---such as ad revenue sharing, algorithmic visibility, or reputation systems---influence the quality and quantity of content that users produce \citep{krautresnick, luca2015socialmedia, aridor2024}. However, direct financial mechanisms such as requiring users to pay a fee to post or allowing peer-to-peer payments between users are rare in the field and thus remain largely understudied. This is especially true in the market for online discussion platforms, since each individual post in a discussion platform like Reddit or X is typically of sufficiently low value that it is not worth the transaction costs to introduce payments into these systems. 

Yet, there is good reason to believe that direct payment mechanisms could meaningfully influence user behavior and content quality on discussion platforms. Signaling theory suggests that posting costs can serve as a screening device, deterring low-quality contributions while allowing users with high-quality content to signal their type by paying the cost \citep{joseph2008email}. Empirically, \citet{tchernichovski2019pnas} showed that introducing a small fee to an online rating system filtered out low information signals and increased the correlation between review ratings and quality. Other empirical studies have found that financial incentives in the form of revenue sharing can influence the quantity and quality of user-generated content  \citep{sun2013blogs, elkomboz2023youtube, kerkhof2024youtube}. However, none of these studies have investigated the behavioral effects of posting fees and direct peer-to-peer payments in a naturally occurring discussion platform. 

One reason direct payment mechanisms have not been more widely adopted is frictions in the payments infrastructure. The value of any individual contribution is typically too small to justify credit card transaction fees, and international platforms face additional frictions related to currency exchange and cross-border banking regulations. However, the emergence of low-cost digital payment rails, such as Bitcoin's Lightning Network, has made it easier for platforms to integrate micropayments into their core design, opening the door to incentive structures that were previously impractical.\footnote{The Lightning Network is a decentralized payments network that is built on top of Bitcoin. It enables faster and lower cost Bitcoin transactions than the base layer would allow. It works by letting users maintain peer-to-peer payment channels that allow them to ``float'' Bitcoin between each other indefinitely, like keeping a bar tab, until final settlement occurs on the base layer. Users can pay others with whom they have no direct channel by routing payments through other channels, usually at a small percentage fee.}

This paper provides empirical evidence on how micropayment incentives shape user behavior, using data from a Bitcoin-based discussion platform called Stacker News. Stacker News is an internet discussion forum---similar in format to Hacker News or Reddit---that integrates Bitcoin micropayments into its core design through the Lightning Network. Users must pay a fee denominated in Bitcoin, usually on the order of 1-100 satoshis (about 0.1 to 10 cents at the time the research was conducted), to post content in any of the platform's topic-specific sub-forums, called territories.\footnote{A satoshi (or sat) is 1/100,000,000th of a Bitcoin. At the time the research was conducted, 1,000 sats was worth about USD \$1.} Users can also send each other peer-to-peer Bitcoin micropayments, called ``zaps'', to reward each other for content that they value. The combination of posting fees and peer-to-peer tipping creates a setting in which both the cost and reward sides of content production are mediated by real financial transactions, making Stacker News a natural field setting for studying how direct payment incentives influence user behavior on discussion platforms.

We exploit variation in posting fees across territories and over time to estimate how the quantity and quality of posts change in response to a territory fee change. Using a difference-in-differences framework with territory and time fixed effects, we find that doubling the posting cost in a territory reduces the number of posts by \gn{PostsCostDoublingEffect}\%, but increases the quality of posts---measured by tips received from other users---by \gn{Zaps48CostDoublingEffect}\%. Because territory operators can change posting fees endogenously, a central empirical concern is whether operators tend to change fees during periods when quantity is already trending down or when quality is already trending up. We conduct event study and pre-trends analysis to verify that this is not the case; indeed, the behavioral response follows the fee change rather than precedes it. The results are consistent with a screening model in which users with low-quality contributions are unwilling to pay the higher cost to post, while users with high-quality contributions are willing to pay the higher cost.

Beyond the cost-based screening mechanism, we investigate whether users learn from and respond to observed tip feedback. To do this, we grouped the posts into different types and measured the expected tip reward for each type under different assumptions about each user's information environment. We find that users are more likely to make a post of a given type when the expected tip reward for that type is high relative to the expected tip rewards for the other types. In other words, users respond to observed tip feedback by shifting the posts they make towards better-rewarded types. The effect is moderated by the user's experience level. More experienced users respond less sharply to observed tip feedback, suggesting that learning takes place early when their beliefs are more diffuse, consistent with prior work on social learning \citep{conley2010}. Moreover, we find that users respond more sharply to tip feedback on their own posts than to feedback on other users' posts, suggesting that feedback on their own posts is more salient than feedback on other users' posts. In the aggregate, we find that the composition of post types has shifted towards the better rewarded types over time, thus showing the effect of tip-driven learning on aggregate post quality.

Lastly, we investigate whether financial incentives shape the composition of active users over time. We find that users who are unable to earn enough tips to cover their posting costs are more likely to exit the platform, while users who earn more tips than they pay in posting fees are more likely to stay. This results in a temporal selection mechanism which could further improve content quality over time.

Our findings are both surprising and unsurprising. They are unsurprising in the sense that the behavioral responses to the financial incentives observed are exactly what economic theory would predict. Demand curves slope downwards, signaling theory works, and people learn from feedback. The results are surprising in the sense that the behavioral responses are detectable and robust for even very small financial incentives, on the order of 5 to 10 cents, in a natural field setting. 

Our findings have policy implications for designers and regulators of user-generated content platforms. The results suggest that content quantity and quality are mediated by financial incentives, even very small ones. Direct  costs to participate can be used to screen out low quality content, while peer-to-peer tipping incentives the production of higher quality content. While our setting is a single platform with a highly selected user community, the underlying mechanisms we identify---cost-based screening, tip-driven learning, and profitability-based selection---are general features of micropayment systems and could plausibly operate on other platforms that adopt similar designs.

%Cost-based screening may become especially relevant as platforms seek to discourage AI-generated content submissions. Our results may therefore offer practical guidance to platform designers and regulators considering the integration of direct payment features.


%\subsection{Related literature}

%Our paper relates to a substantial literature on the economics of platform design and user-generated content (UGC). \citet{luca2015socialmedia} surveys the economics of UGC, documenting how quality is shaped by promotional content, peer effects, contributor biases, and self-selection into the decision to contribute, noting that non-pecuniary incentives are often used to steer contributions. \citet{ghosh2011incentivizing} provide a game-theoretic model of UGC incentives in which contributors are strategic and motivated by exposure, showing that when exposure is independent of quality, platforms will be flooded with low-quality content. This paper speaks to their findings by showing what happens when quality is financially incentivized and when contributions are screened by an entry fee. \citet{ghosh2014rankorder} extend this framework to rank-order mechanisms, analyzing how platforms can use ranking systems to incentivize effort, which is relevant to how Stacker News uses zap-based rankings to surface content. \citet{liu2021money} develop a model showing that monetary incentives can either increase or decrease UGC contributions depending on heterogeneity in contributor motivation. Our work provides an empirical test of the net effect of direct monetary incentives, plus additional findings regarding the effect of entry fees.

%On the empirical side, \citet{muchnik2013social} demonstrate in a large-scale randomized experiment that prior positive social signals create significant herding effects on subsequent ratings, raising important questions about whether peer-generated evaluations reflect true quality or social influence. Our use of zaps as a quality measure is subject to similar concerns, though the fact that zaps on Stacker News require real monetary outlays may mitigate the bias relative to costless upvote systems. \citet{chen2010comparisons} conduct a field experiment on MovieLens showing that social comparisons (informing users about how their contribution levels compare to other users) significantly increases contributions. Our finding that users learn from their personal zap history (Section \ref{sec_v4v}) extends this insight by showing that financial feedback can also drive higher effort, in addition to social feedback. Relatedly, \citet{paridar2025} study online tipping on a UGC platform and show that tipping behavior is shaped by evolving social norms and information disclosure. Our contribution differs in that we study a platform where tipping is combined with mandatory posting costs, allowing us to examine both the reward side and the cost side of micropayment incentives.

%The design of digital payments systems is also relevant to our setting. \citet{aukauffman2008mobile} analyze the economics of mobile payment adoption, identifying transaction costs, network effects, and stakeholder incentive alignment as key determinants of whether new payment technologies achieve viability. The emergence of Bitcoin's Lightning Network has substantially reduced the transaction cost barriers they identified, making the kind of micropayment-mediated platform we study technically feasible at scale. \citet{krautresnick} synthesize social science research on online community design, offering theory-grounded design principles for encouraging contributions and regulating behavior. Their framework highlights the role of financial and reputational incentives in sustaining communities, but they note that direct financial mechanisms remain largely untested in practice---a gap our study helps fill. Lastly, \citet{treiblmaier2021ecra} provide a list of salient research topics for how blockchain can impact e-commerce. Our findings speak directly to their suggested topics O2 (``how does blockchain impact business models of e-commerce companies''), O3 (``how does blockchain impact organizational structures and value networks of e-commerce companies''), and C4 (``how does blockchain impact segmentation, personalization, and customization in e-commerce'').









