\section{Cost-based screening}\label{sec_pay_to_post}

In this section, we consider our first hypothesis: whether higher posting costs lead to fewer posts in a territory, but higher quality posts. 

\subsection{Evidence on post quality}

To test the relationship between posting fee and post quality, we run regressions of the following form:
\begin{align}
\ln \text{Quality}_{ijt} = \alpha \ln \text{Cost}_{ijt} + \delta_{j} + \gamma_{t} + \epsilon_{ijt} \label{eq_qual_reg}
\end{align}
where $i$ indexes a post, $j$ indexes a territory, and $t$ indexes a year-week.\footnote{For example, 2024w1 is a different $t$ than 2025w1.} $\text{Quality}_{ijt}$ is the measure of post quality, $\text{Cost}_{ijt}$ is the cost (in sats) of the post, $\delta_{j}$ is a set of dummy variables for each territory, and $\gamma_{t}$ is a set of dummy variables for each week. The coefficient $\alpha$ identifies the elasticity between posting cost and post quality.\footnote{In practice, we add 1 to post quality and posting cost to avoid taking logs of zero. Since the means of both variables are well above one, the $\ln(1+x)$ transformation closely approximates $\ln(x)$, and the coefficients retain their interpretation as elasticities.} We hypothesize that $\alpha > 0$.

To measure post quality, we measure the number of sats the post earned on zaps in the first 48 hours of posting. Zaps represent a revealed preference measure of quality, since users must pay real money to zap. The purpose of the dummy variables is to absorb any unobserved heterogeneity in territories (e.g. if some territories are more popular and thus attract more zaps), and to absorb any global time trends in the popularity of Stacker News or the generosity of its users.

The effect of posting cost is identified from differential changes in post quality across territories when the territory posting costs change differentially. For example, if the posting cost in the \texttt{econ} territory increases while the posting cost in \texttt{bitcoin} stays the same, and subsequently the average quality of posts increases in \texttt{econ} relative to that in \texttt{bitcoin}, this would suggest that the change in posting cost likely caused the change in post quality. The coefficient $\alpha$ is identified off the many such changes present in the data.

To give the reader a sense of the variation in posting costs, we plot the posting cost histories for four representative territories in Figure \ref{fig_posting_fee_histories}. The figure shows that there is indeed substantial variation in posting fees both across and within territories. 
%Altogether, the data contains \gn{NumPostingFeeChanges} changes in territory posting fees across the \gn{NumTerritories} territories. 

Before running the regression, we apply the following sample selection criteria. We do not include posts in territories that are run by Stacker News itself for special purposes.\footnote{This includes territories like the \texttt{jobs} territory, which companies (usually Bitcoin-focused companies) can make job postings, or the \texttt{AMA} territory, where influential people are invited to make ``Ask Me Anything'' posts.}  We also do not include a number of special post types that do not follow normal posting rules.\footnote{These include profile posts, which users can post and edit for free, ``saloon'' posts, which are daily discussion threads posted by Stacker News, and freebies---a limited number of reduced-visibility posts that users are allowed to make for free.} Lastly, we do not include any posts made in territories by the territory operator. Since 70\% of posting costs go to the territory operator, the incentives for territory operators to post in their own territories differ from that of non-operators. In the data we use for the regression, the average posting cost is \gn{AvgPostingCost} sats, the average amount of sats earned in the first 48 hours is \gn{AvgSats48} sats, and the average number of comments in the first 48 hours is \gn{AvgComments48}. There is substantial variation in all three: the standard deviation of the posting cost is \gn{SdPostingCost} sats, of sats earned in the first 48 hours is \gn{SdSats48}, and of comments in the first 48 hours is \gn{SdComments48}. 


Table \ref{tbl_sats48_cost_reg} shows results for regressions of specification \eqref{eq_qual_reg} where post quality is measured as zaps in the first 48 hours. Each column of Table \ref{tbl_sats48_cost_reg} includes a different set of fixed effects in the regression. Column 1 includes no fixed effects, and is therefore a straight OLS regression of log zaps in the first 48 hours on log posting cost. Column 2 includes territory and week fixed effects to control for any heterogeneous effects between territories. Column 3 includes fixed effects for the identity of the territory operator to control for any differential zapping behavior between territory operators. For example, some territory operators zap every post that comes into their territory while others do not. Territory-operator fixed effects control for this behavior.\footnote{Note that territory fixed effects do not fully absorb territory operator fixed effects, since a single user can own multiple territories, and territories can also change operators over time.} Finally, column 4 includes user fixed effects to test whether the gains in post quality are driven by within-user effects or compositional effects. 

Table \ref{tbl_sats48_cost_reg} shows that there is a statistically significant and robust positive relationship between territory posting fees and post quality as measured by zaps in the first 48 hours. In terms of the magnitude of the effect, Table \ref{tbl_sats48_cost_reg} column 3 (our preferred specification) suggests that the elasticity between territory posting cost and expected post quality is \gn{Zaps48CostElasticity}. This roughly translates to: if a territory doubles its posting cost, then the quality of posts is expected to increase by \gn{Zaps48CostDoublingEffect} percent. The relationship is not explained by territory specific effects, such as a spurious correlation between posting fees and the popularity of a territory's topic, nor is it explained by global time trends in posting fees and zap behavior on Stacker News. Neither is it explained by effects related to territory operators---for example, if territory operators who set high fees also tend to zap posts in their territory more generously. The best explanation for the correlation between posting cost and post quality is that users will only choose to post in a higher cost territory if they think that the post is of high enough quality to warrant the cost. This is consistent with  users' self-reported perceptions of their own behavior on the platform. One Stacker News user is quoted saying: 

\begin{quote}
``If I put a lot of effort into a post, I know that the posting fee will be offset by the zaps. And even if it doesn't, I'm just happy to show the work I've done and I'm ready to pay for it. On the other hand, when I share a simple link with a few quick comments and quotes, it takes me a few minutes, and I look for the cheaper territory to post it. If I don't find any cheap territory, I'd rather not post, as I don't think paying to post links is worth the same as paying to post for [my] actual proof-of-work.''\footnote{In this statement, the user is referring to link posts, which are posts that include a link to an external URL, often without any text in the post body. Link posts usually receive less zaps and are considered to be of lower quality because the content is not produced by the user themselves, and are thus less rewarded by zaps.}
\end{quote}

%\noindent It makes sense that users will only be willing to pay a high posting cost if they think the quality of the post justifies it---either because they will recuperate the cost through zaps or because of a stronger intrinsic desire to post high quality work. However, one may wonder why users don't just choose a low cost territory to post in. There is no rule on Stacker News that says users must post content in the most relevant territory. Moreover, most territories on Stacker News are lightly moderated, so posting content to an irrelevant territory is not likely to result in post removal. Despite these caveats, in practice we observe that users tend to post in territories for which the content is most relevant. This may be for a few reasons. First, users can subscribe to or mute territories.\footnote{Subscribing to a territory means the user will receive notifications when a new post is made to that territory. Muting a territory means that the user will no longer see posts from that territory.} Thus, posting in a more relevant territory will increase the visibility of the post to users who are most likely to be interested in it. Second, territory operators sometimes add value to their territories by collecting, summarizing, and rewarding top posts. A post is less likely to be highlighted if it is not relevant to the territory. Lastly, users may have an intrinsic, aesthetic desire to post in the most relevant territory, especially if they view their content to be of high quality.\footnote{In terms of the model, this would be reflected in a high positive affiliation between the territory specific components of $(q_j, \epsilon_j)$.}

Finally, we comment on column 4 of Table \ref{tbl_sats48_cost_reg}, where we include user fixed effects. The inclusion of user fixed effects reduces the estimated elasticity between posting cost and post quality from \gn{Zaps48CostElasticity} to \gn{Zaps48CostElasticityUserFE} (still statistically significant at the 5\% level). This suggests that the increase in post quality in response to an increase in posting cost is driven by both intensive margin (within-user) and extensive margin (compositional) effects. On the intensive margin, the same users now make higher quality posts, conditional on posting. On the extensive margin, the composition of posters in the territory shifts towards higher quality, most likely due to lower quality users dropping out. Column 3 remains our preferred specification over column 4, because we view the effect on the composition of users as a dimension we want to capture when studying the relationship between posting cost and post quality.

%Next, we present results when the number of comments in the first 48 hours is used to measure quality instead of the number of zaps. The results are presented in Table \ref{tbl_comments48_cost_reg}. As with zaps, Table \ref{tbl_comments48_cost_reg} demonstrates that there is a robust and statistically significant positive relationship between territory posting cost and the number of comments a post receives in the first 48 hours. Table \ref{tbl_comments48_cost_reg}  column 4 implies that when territory posting cost doubles, the number of replies a post in that territory is expected to receive in the first 48 hours increases by \gn{Comments48CostDoublingEffect} percent. 

\subsubsection{Event study analysis}

Our empirical setting is similar to a difference-in-differences (DID) regression, because we are identifying the effect of territory fee changes from the change in post quality following the fee change, while allowing for baseline differences between territories and common time trends in post quality. In classical DID, an important assumption is that the average post quality in a territory does not systematically trend upwards prior to a post fee change. If it did so, that would call into question whether the timing of the fee change is endogenous to some prior effect that was already increasing quality. Our setting is a little more complicated than a classical DID because we have multiple fee changes in a territory, bidirectional fee changes, and continuous variation in the size of the fee change. Nevertheless, it would be useful for us to test whether there are any systematic post quality changes prior to a fee change.

To test this, we run the following regression:
\begin{align}
\ln \text{Quality}_{ijt} = & \sum_{s=-12}^{12} \alpha_{s}^{+} 1\left[ \Delta \text{Cost}_{j,t-s}>0 \right] \nonumber \\
& + \sum_{s=-12}^{12} \alpha_{s}^{-} 1\left[ \Delta \text{Cost}_{j,t-s} < 0 \right] + \delta_j + \gamma_t + \epsilon_{ijt} \label{eq_post_quality_event_study}
\end{align}
Here $\Delta\text{Cost}_{jt}$ is a continuous variable for how much the posting cost in territory $j$ changed in week $t$, and $1\left[\Delta\text{Cost}_{jt} \gtrless 0\right]$ is an indicator for whether the posting cost in territory $j$ increased/decreased in week $t$. Thus, $\alpha_{s}^{+/-}$ measures the contribution to post quality of being $s$ weeks away from a posting cost increase/decrease when $s<0$, and the contribution to post quality of being $s$ weeks after a posting cost increase/decrease when $s>0$. 

We estimate equation \eqref{eq_post_quality_event_study} and plot the estimates for $\alpha_{s}^{+/-}$, along with their 95\% confidence intervals, in Figure \ref{fig_post_quality_event_study}. The left panels show the results for a specification in which user fixed effects were not included, and the right panels show the results for a specification in which user fixed effects were included.

Figure \ref{fig_post_quality_event_study} shows that there was no systematic upward trend in post quality prior to post fee increases. After a post fee increase, we see that post quality begins to trend upwards. By comparing the top left and top right panels, we also see that including user fixed effects moderates the effect, but does not eliminate it---suggesting the presence of both compositional and intensive margin effects. Although noisier, we find a similar result surrounding decreases in post fees. There is no systematic downward trend in post quality prior to post fee decreases, and following a post fee decrease post quality begins to trend slightly downwards. 



\subsection{Evidence on post quantity}

Now we consider whether territory posting cost also influences the number of posts a territory receives. If users are sensitive to posting cost, then we expect that territory posting fee will be negatively correlated with number of posts. To test this, we run regressions of the following form:
\begin{align}
\ln \text{Posts}_{jt} = \alpha \ln \text{Cost}_{jt} + \delta_{j} + \gamma_{t} + \epsilon_{jt} \label{eq_quant_reg}
\end{align}
where $j$ indexes a territory and $t$ indexes a week. $\text{Posts}_{jt}$ is the number of posts posted in territory $j$ in week $t$, $\text{Cost}_{jt}$ is territory $j$'s posting fee in week $t$ (measured as the average across days), $\delta_j$ is a set of territory fixed effects, and $\gamma_{t}$ is a set of week fixed effects. The results of this regression, for various combinations of fixed effects, are presented in Table \ref{tbl_posts_cost_reg}. As expected, there is a robust and statistically significant negative relationship between territory posting cost and the quantity of posts in a territory. Using column 3 as our preferred specification, the results imply an elasticity of post quantity with respect to post cost of $\gn{PostsCostElasticity}$. This translates to: if the posting cost doubles, the territory can expect to receive \gn{PostsCostDoublingEffect} percent fewer posts per week. 

\subsubsection{Event study analysis}

We now turn to an event study analysis to test whether there are systematic changes in post quantity prior to territory fee changes. We run the following regression:
\begin{align}
\ln \text{Posts}_{jt} = & \sum_{s=-12}^{12} \alpha_{s}^{+} 1\left[ \Delta \text{Cost}_{j,t-s}>0 \right] \nonumber \\
& + \sum_{s=-12}^{12} \alpha_{s}^{-} 1\left[ \Delta \text{Cost}_{j,t-s} < 0 \right] + \delta_j + \gamma_t + \epsilon_{ijt} \label{eq_post_quantity_event_study}
\end{align}
The notation and logic is much the same as in \eqref{eq_post_quality_event_study}, so we will not repeat ourselves here. Figure \ref{fig_post_quantity_event_study} shows the estimated values for $\alpha_{s}^{+/-}$ and their 95\% confidence intervals. 

Figure \ref{fig_post_quantity_event_study} shows that there is no systematic decrease in post quantity prior to a territory fee increase. If anything, there appears to be a systematic upward trend in post quantity prior to fee increases, followed by a downward trend in post quantity after the fee increase. For negative fee changes, there appears to be a slight systematic downward trend in post quantity prior to a fee decrease, followed by an upward trend in post quantity after a fee decrease.

Comparing Figures \ref{fig_post_quality_event_study} and \ref{fig_post_quantity_event_study} reveals a pattern that is consistent with our hypothesized mechanism. Prior to a fee increase, post quantity trends upwards while post quality remains flat. The absence of a pre-trend in quality indicates that quality improvements observed after a fee increase are not the continuation of a pre-trend that was already underway. Rather, quality begins to rise only after the fee change takes effect, consistent with a cost-based screening mechanism. The rising quantity prior to a fee increase suggests that territory operators may be raising fees in response to growing volume, with the quality improvement emerging as a consequence of the higher fees screening out lower quality posts. The reverse pattern surrounding fee decreases tells a symmetric story. This story appears consistent with how some territory operators on the platform have described their rationale for fee changes. One territory operator is quoted saying:

\begin{quote}
``For \texttt{science}, I only experimented very little at the beginning. Don't remember the specifics, but I must have tried really low (like 10-20 sats) and then a bit higher (like 100 sats). Because I had a personal policy of upvoting each post that had a modicum of quality (e.g. not just a link without context), I ended up with a small army of posters (assmilkers) that were doing the bare minimum but not enough to instigate comments or discussions. I think the reason for the 100 sats was to see how this increase would affect the willingness of those low-effort posters to post. It worked, but a side effect is that I was getting much less volume, also from quality posters. So I put it back down, and just let the community decide if a post is worth getting sats.''
\end{quote}

\noindent This operator's reasoning reflects awareness of the cost-based screening mechanism as a tool for managing post quantity and .

\subsection{Discussion}

Taken together, the results are both surprising and unsurprising. They are unsurprising in the sense that they conform with economic theory: demand curves slope downwards (when posting costs go up, number of posts goes down), and signaling theory works (when posting costs go up, higher quality posts are made). They are surprising in the sense that even such small micro-incentives (the average posting cost is just \gn{AvgPostingCost} sats, or about \gn{AvgPostingCostCents} cents) are enough to influence user behavior in such a way that post quality is improved. The results suggest that even very small posting fees can meaningfully affect the quantity-quality tradeoff in online discussion platforms.  
%Moreover, the assumptions required for this result to hold more broadly are fairly weak: we require only that expected rewards are increasing in post quality (Assumption \ref{asm_monotonicity}), that post quality and intrinsic motivation to post are positively affiliated (Assumption \ref{asm_mlrp}), and that extreme levels of intrinsic motivation are sufficiently rare (Assumption \ref{asm_logconcavity}). All three assumptions are likely to hold on other platforms where micropayment mechanisms could be introduced, suggesting that these findings may generalize beyond our specific setting. However, Stacker News is a highly selected group of individuals organized around a shared interest in Bitcoin, so caution is advised in extrapolating these results to other settings.



